How Important are Usage Examples in REST API Documentation?

### 2017-01-29 bare_conf.tex
author names

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Michael Shell}
\IEEEauthorblockA{School of Electrical and\\Computer Engineering\\
Georgia Institute of Technology\\
Atlanta, Georgia 30332--0250\\
Email: http://www.michaelshell.org/contact.html}
\and
\IEEEauthorblockN{Homer Simpson}
\IEEEauthorblockA{Twentieth Century Fox\\
Springfield, USA\\
Email: homer@thesimpsons.com}
\and
\IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
\IEEEauthorblockA{Starfleet Academy\\
San Francisco, California 96678--2391\\
Telephone: (800) 555--1212\\
Fax: (888) 555--1212}}

@@

\section{Introduction}
\section{Methodolody}
\subsection{Research Goals} % (fold)
\subsection{Requirements} % (fold)
\subsection{Study Object} % (fold)
\subsection{Study Design} % (fold)
\subsubsection{Tasks} % (fold)
  For each task, define the task. Information that provided to the participants and what is required to perform it successfully.

>>>>

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{S M Sohan, Frank Maurer\IEEEauthorrefmark{1}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}
Dept. of Computer Science\\
University of Calgary\\
Canada\\
\{smsohan, frank.maurer\}@ucalgary.ca}
\and
\IEEEauthorblockN{Craig Anslow}
\IEEEauthorblockA{School of Eng. and Computer Science\\
Victoria University of Wellington\\
New Zealand\\
craig@ecs.vuw.ac.nz}
\and
\IEEEauthorblockN{Martin Robillard}
\IEEEauthorblockA{
School of Computer Science\\
McGill University\\
Canada\\
martin@cs.mcgill.ca}
}

@@

\section{Introduction}
\section{Methodolody}
\subsection{Research Goals}

This research is aimed at answering the following research questions:

\begin{itemize}
  \item What impact does usage examples have on REST API client developer productivity?
  \item What what problems API client developers face when using a REST API where documentation lacks usage examples?
\end{itemize}

\subsection{Requirements} % (fold)
\subsection{Study Object} % (fold)
\subsection{Study Design} % (fold)
\subsubsection{Tasks} % (fold)
  For each task, define the task. Information that provided to the participants and what is required to perform it successfully.
